Reproducible Validation and Replication Studies in Nanoscale Physics

### 2021-01-31 tex/discussion.tex
fix typos found in proof

Validation has been a hard goal to achieve for our solver since the field does not have benchmarks that are meant to be used for validation. Multiple times,
we encountered experimental results that we aspired to replicate, but due to the insufficient reporting of the experimental conditions, the setup and the geometries involved, 
we have been unable to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al., made 
the validation possible.

>>>>

Validation has been a hard goal to achieve for our solver since the field does not have benchmarks that are meant to be used for this purpose. Multiple times,
we encountered experimental results that we aspired to use for validation, but due to the insufficient reporting of the experimental conditions, the setup and the geometries involved, 
we have been unable to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al., made 
the validation possible.

### 2021-01-31 tex/results.tex
fix typos found in proof

To be able to replicate the result of Figure S4 of the supplementary materials of Ellis et al., we
need to identify the lower-frequency mode for each of
the aspect ratios in our computations. For each aspect ratio ($AR$) 
value from 1 to 7, we computed the extinction cross-section $C_{ext}$ across the wave numbers in the range
800--1000 cm$^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$ nm) and varied length ($L=400$--$2800$ nm), for normal 
and 22-degrees angle of incidence. The simulations where performed 
for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
the lowest mode that is not a longitudinal one and extracted its wavelength (see Table \ref{tab:ar_peaks}) to replicate 
Figure \ref{fig:rep_FS4_ellis}. This figure shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
(Note that Ellis et al.\ changed the angle of incidence of the illuminating vector while in \pygbe we 
rotated the geometry instead.)

@@

The results of Figure 2a in Ellis et al.\ were obtained on a pillar of aspect ratio $AR=4$. For this case,
we have the original mesh, provided to us by the authors. We also know that our computation 
for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
attempted to validate our simulations with their experimental results (red curve on their paper), as well 
as to replicate their simulations (green curve on their paper).
Figure 2a of Ellis et al.\ presents measured and simulated reflectances of SiC pillar
arrays with a 500-nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated size of the pillar.

>>>>

To be able to replicate the result of Figure S4 of the supplementary materials of Ellis et al., we
need to identify the lower-frequency mode for each of
the aspect ratios in our computations. For each aspect ratio ($AR$) 
value from 1 to 7, we computed the extinction cross-section $C_{ext}$ across the wave numbers in the range
800--1000 cm$^{-1}$. We identified the lower-frequency mode ($E^{\parallel}_{100}$ for Ellis et al.) that is not a 
longitudinal mode. The longitudinal modes appear only when we have an incidence angle that is off-normal, since 
they are associated with the height of the pillar. Figure \ref{fig:AR_22_vs_norm} shows the results of the extinction 
cross-section of a SiC pillar of fixed height ($H=950$ nm), fixed width ($W=400$ nm) and varied length ($L=400$--$2800$ nm), for normal 
and 22-degrees angle of incidence. The simulations were performed 
for the long-edge orientation, meaning that the electric field is aligned with the length of the pillar 
when having normal incidence as shown on Figure \ref{fig:ellis_ang_inc}. From these results, we selected 
the lowest mode that is not a longitudinal one and extracted its wavelength (see Table \ref{tab:ar_peaks}) to replicate 
Figure \ref{fig:rep_FS4_ellis}. This figure shows the results from  Ellis et al. (digitized by hand using the WebPlotDigitizer) and the results obtained
with \pygbe, and Table \ref{tab:err_AR} shows that the percentage error is below 2$\%$ for all cases.
(Note that Ellis et al.\ changed the angle of incidence of the illuminating vector while in \pygbe we 
rotated the geometry instead.)

@@

The results of Figure 2a in Ellis et al.\ were obtained on a pillar of aspect ratio $AR=4$. For this case,
we have the original mesh, provided to us by the authors. We also know that our computation 
for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
attempted to validate our simulations with their experimental results (red curve on their paper), as well 
as to replicate their simulations (green curve on their paper).
Figure 2a of Ellis et al.\ presents measured and simulated reflectances of SiC pillar
arrays with a 500-nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated side of the pillar.
